---
title: "IPEG_analysis"
author: "Bruce Peng"
date: "30/03/2020"
output: html_document
---

Here includes codes for analysis of IPEG.

**Participants and trial numbers:**
A total of 30 participants are included in this dataset, each participants completed 40 trials thus the total number of trials is 40x30 = 1200. 34 trials were deleted due to participants' written responses did not conform to the task criteria. Thus, the total number of trials included in the analysis is 1166. 

**Data description:**
*Participant:* N=30
*Story_ID:* Story presented to participants on each trial, a total of 40 stories were presented. These stories can be found in IPEG_stimuli.xlsx
*STFace_ID*: Simulation target ID 
*ST_gender*: Sex of Simulation target (F=Female, M=Male). Note: no age varaible was recorded for simulation targets as they were all in the young age group.
*HTFace_ID*: Helping target ID
*HT_gender*: Helping target sex (Male or female)
*HT_age*: Helping target age (Old or young)
*Sex:*: Participants' sex, Male or Female
*Match*: Age and sex match of simulation and helping targets (1=Sex and age mismatch, 2= Sex mismatch and Age match, 3= Sex match and Age mismatch, 4= Sex and age match)
*Trial:* Trial order presented to participants.
*Condition:* Imagine helping (Experimental:Imagine) and identify journalistic technique (Control:Identify)
*Detail:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(simple)-7(detailed) Likert scale. 
*Coherence:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(vague)-7(coherent and clear) Likert scale. 
*Perspective:*  "When you identified the media website, imagined helping, or visualized the media website and comments  did you consider  the thoughts and feelings of the person?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (strongly considered). 
*Help:* DV of interest. "How likely would you be to help in this situation?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (very willing) Likert scale.

Note: Detail, Coherence and Perspective are included so the proctocol mirrored previous studies as closely as possible and are not of particular interest in the current study. 

*Emotional reaction:*
Emotional reaction (collected for all conditions) rated on a 1(not at all)-7(very strongly) Likert scale for the following emotions:
-	Soft-hearted
-	Troubled 
-	Warm 
-	Distressed
-	Sympathetic
-	Compassionate
-	Disturbed
-	Tender
-	Moved
-	Worried
These measures are included to reduce the possibility of participants correctly guaging the experimental goal and are not utilized in the analyses


# Package and directory set up
```{r setup, include=FALSE}
# Load packages
if (!require(pacman)) install.packages('pacman')
pacman::p_load(sjstats,sjPlot,lme4,lmerTest,emmeans,ggeffects,tidyverse,MuMIn,brms, bayestestR) 

# source custom codes
source("C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/source/Bayes_scripts.R")
source("C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/source/LMM_scripts.R")

# ggplot colours
palette <- c("#eeaa7b", "#00b159", "#00aedb", "#F8766D", "#9590FF", "#CC9933", "#0000FF")
```

##Data setup

```{r}
# Loading data
IPEG.df<- read.csv('IPEG_fulldata_N=30.csv', header=T)

# Remove deleted trials from data frame
IPEG.df<- IPEG.df[complete.cases(IPEG.df$Condition),]

# Convert Story_ID and Condition vectors into factors and ensure Identify condition is set as the reference group
IPEG.df$Story_ID<- as.factor(IPEG.df$Story_ID)
IPEG.df$Conditions<- as.factor(IPEG.df$Conditions)
levels (IPEG.df$Conditions) <- c('Identify', 'Imagine')

# Data transformations 
## Generate the five factor variable for Match conditions
IPEG.df$Match_condition<- IPEG.df$Match + 1
IPEG.df$Match_condition[IPEG.df$Conditions=="Identify"] <- 1
IPEG.df$Match_condition <- as.factor(IPEG.df$Match_condition)
levels(IPEG.df$Match_condition) <- c("Identify","S-A-", "S-A+","S+A-", "S+A+")

## Effect code and dummy
IPEG.df<- IPEG.df%>% 
              mutate(
                # Effect code sex of helping targets(Female=1, male=-1)
                HT_sex_c= ifelse(HT_sex=='F', 1, -1),
                # Effect code age of helping targets (1=Old, -1=Young)
                HT_age_c = ifelse(HT_age=='Old', 1, -1),
                # Create a dummy variable= for the condition variable
                dummy_img = as.numeric (Conditions=='Imagine'),
                Coherence_C = group_center(Coherence, participant),
                Detail_C = group_center(Detail, participant))

# Set up Back difference coded
IPEG.df<- IPEG.df%>% 
              mutate(
                backdiff_2v1 = ifelse (Match_condition=="Identify",-0.8, 0.2),
                backdiff_3v2 = ifelse(Match_condition=="Identify"|Match_condition=="S-A-", -0.6, 0.4),
                backdiff_4v3 = ifelse(Match_condition=="S+A-"|Match_condition=="S+A+", 0.6, -0.4),
                backdiff_5v4 =ifelse (Match_condition=="S+A+",0.8, -0.2))

# Create dummy coded variables, set reference group as Identify
IPEG.df<- IPEG.df %>% 
              mutate(
                dummy_SAMM = as.numeric(Match_condition=="S-A-"),
                dummy_SMMAM= as.numeric(Match_condition=="S-A+"),
                dummy_SMAMM = as.numeric(Match_condition=="S+A-"),
                dummy_SAM =as.numeric(Match_condition=="S+A+"))


# vividness df
vivid.df <- IPEG.df %>%
                filter(Conditions == 'Imagine')
```


# Frequentist Linear Mixed Modeling

## Main effect analysis
### Determine if clustering exist
```{r}
ranova(lmer(Help~(1|participant)+(1|Story_ID) +(1|STFace_ID)+(1|HTFace_ID), data=IPEG.df))
# Only STFace_ID is not significant (a= 0.2) so include HTFace_ID, participant and Story_ID as varying effects
```

### Overall Generalizability of Prosoical simulation effect
```{r}
step(lmer(Help~Conditions+HT_sex_c+HT_age_c+(dummy_img||participant)+(dummy_img||Story_ID) +(dummy_img||HTFace_ID), data=IPEG.df))
zcp_model_rm<-lmer(Help~Conditions +HT_sex_c+HT_age_c+(dummy_img||participant)+(1|Story_ID) +(1|HTFace_ID), data=IPEG.df)
final_model<- lmer(Help~Conditions+HT_sex_c+HT_age_c+(dummy_img|participant)+(1|Story_ID) +(1|HTFace_ID), data=IPEG.df)
anova(zcp_model_rm,final_model, refit=F)

# Results
anova(final_model, ddf='Kenward-Roger')
# Extract means for each conditions
(posthoc<- emmeans(final_model, pairwise~Conditions))
confint(posthoc)
# Effect size
r.squaredGLMM(final_model)
```
#### Plots
```{r}
# Condition differences in willingness to help
means<- data.frame(posthoc$emmeans)
bar_plot(means)

# Plot individual differences in the prosocial simulation effect in absolute scale using 
final_model2<- update(final_model, .~. -Conditions +dummy_img)
plot<-coef(final_model2)$participant[4]
plot(x= seq(1:30),y= plot$dummy_img, xlab='Participants', ylab="Imagine condition random slopes");abline(0,0, col='red');abline(final_model2@beta[4],0, col='blue')
```
#### Assumption testing
```{r}
# Normality, homogeneity of variance etc
plot_model(final_model, type='diag')
# Random effects in the deviation scale
plot_model(final_model, type='re')
```

## Generalizability of Prosoical simulation effect by age and sex
### Back Difference coding
#### Analysis
```{r}
zcp_step1<-step(lmer(Help~Match_condition+HT_sex_c+HT_age_c+(backdiff_2v1+backdiff_3v2+backdiff_4v3+backdiff_5v4||participant)  +(backdiff_2v1+backdiff_3v2+backdiff_4v3+backdiff_5v4||HTFace_ID)+(backdiff_2v1+backdiff_3v2+backdiff_4v3+backdiff_5v4||Story_ID), data=IPEG.df, contrast= list (Match_condition= MASS::contr.sdif)))
rm_genmodel<- lmer(Help~Match_condition+HT_sex_c+HT_age_c+(backdiff_2v1+backdiff_5v4||participant)+(1|HTFace_ID)+(1|Story_ID), data=IPEG.df,contrast= list (Match_condition= MASS::contr.sdif))
rm_genmodel<- refit_LMM(rm_genmodel)#3 refits
Gen_model<- lmer(Help~Match_condition+HT_sex_c+HT_age_c+(backdiff_2v1+backdiff_5v4|participant) + (1|HTFace_ID) + (1|Story_ID), data=IPEG.df,contrast= list (Match_condition= MASS::contr.sdif))
anova(rm_genmodel,Gen_model, refit=F)

# Results
anova(rm_genmodel, ddf='Kenward-Roger')
summary(rm_genmodel,ddf="Kenward-Roger")
```





### Dummy coding
#### Analysis
```{r}
zcp_step2<-step(zcp_genmodel2<- lmer(Help~Match_condition+HT_sex_c+HT_age_c+(dummy_SAMM+dummy_SMMAM+dummy_SMAMM+dummy_SAM||participant)  +(dummy_SAMM+dummy_SMMAM+dummy_SMAMM+dummy_SAM||HTFace_ID)+(dummy_SAMM+dummy_SMMAM+dummy_SMAMM+dummy_SAM||Story_ID), data=IPEG.df))
rm_genmodel2<- lmer(Help~Match_condition+HT_sex_c+HT_age_c+(dummy_SAMM+dummy_SAM+dummy_SMAMM||participant)+(1|HTFace_ID)+(1|Story_ID), data=IPEG.df)
rm_genmodel2<- refit_LMM(rm_genmodel2)
gen_model2<- lmer(Help~Match_condition+HT_sex_c+HT_age_c+(dummy_SAMM+dummy_SAM|participant)+ (0+dummy_SMAMM|participant)+(1|HTFace_ID)+(1|Story_ID), data=IPEG.df) 
gen_model2<- refit_LMM(gen_model2)#singular fit, remove correlation  parameter for dummy_SMAMM, after this the truncated model still did not converge so refit one time and converged. 
anova(rm_genmodel2,gen_model2, refit=F)

## Test of fixed effects using F-test
anova(rm_genmodel2, ddf='Kenward-Roger')
(posthoc_gen<-emmeans(rm_genmodel2, pairwise~Match_condition, adjust= 'bonferroni'))
confint(posthoc_gen, adjust='bonferroni')
```
#### Plots
```{r}
# Condition differences in willingness to help
gen_means<- data.frame(posthoc_gen$emmeans)
colnames(gen_means)[1]<- "Conditions"
bar_plot(gen_means)
``` 



# Bayesian Cumulative link mixed model
## Generalization of the prosocial simulation effect 
```{r}
Bayes<- brm(data=IPEG.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+HT_sex_c+HT_age_c+(Conditions|participant)+
                      (Conditions|Story_ID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))

saveRDS(Bayes, file='Bayes.rda')
saveRDS(posterior$b_ConditionsImagine, "IPEG_Imagine.rds")

# Diagnostic Checks: pp check and traceplots
pp_check(Bayes);plot(Bayes)
# Rhat and sample sizes
bayes_samples(Bayes)

# Prior Predictive simulations
set.seed(67);prior_sim(Bayes, c("sd_participant", 'cor_participant', "b"))

# Results
summary(Bayes, prob=0.89)
# pd
p_direction(Bayes, parameters = "b_Conditions")
# % in ROPE
rope(Bayes,ci=1, range = c(-0.10, 0.10), parameters = "b_Conditions")

# Extract posterior samples 
set.seed(67);posterior<- posterior_samples(Bayes) 
latent_SD(posterior)


# OR
posterior_summary(exp(posterior$b_ConditionsImagine), probs=c(0.055, 0.945))
```
### Plots
```{r}
# Violin plots
plot.df<- as.data.frame(posterior$b_ConditionsImagine)
colnames(plot.df)<- "Posterior"
ggplot(plot.df, aes(x=1, y=Posterior))+
                      geom_violin(trim=FALSE)+
                      geom_boxplot(width=0.1, fill="white")+
                      theme_classic()+
                      geom_hline(yintercept=0, linetype="dashed", color = "red", size=0.5) +
                      labs(x="Contrasts", y = expression(beta)) +
                      stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7) + 
                      theme(legend.position = "none") +
                      xlab("Imagine Helping>Identify Media Source") +
                      scale_x_discrete(labels=c(""))


# Plot the predicted probability of each category on the outcome measure for each condition
PSE_plot<-conditional_effects(Bayes,categorical=T)
plot(PSE_plot)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "Imagine Helping")) +
  theme_classic() +
  xlab("Conditions") +
  ylim (0, 0.45)
```

### Contrast PSE across IPE, IPEF and IPEG
```{r}
IPE_imagine.df<-readRDS(file="IPE_Imagine.rds")
IPEF_imagine.df<-readRDS(file="IPEF_Imagine.rds")

# Violin plot of each experiment 
PSE<- cbind.data.frame("IPE"=IPE_imagine.df,
                       "IPEF"=IPEF_imagine.df, 
                       "IPEG"=posterior$b_ConditionsImagine)
PSE.df<- PSE
PSE<- PSE %>% gather("IPE","IPEF", 'IPEG', key= Condition, value= Posterior)
violin_PSE<- violin_bayes(PSE, HDI_range = c(0.055, 0.945))[[1]]
violin_PSE +
  labs(x="Experiment", y = "Logit")+
  scale_x_discrete(labels=c( "Experiment 2", "Experiment 3", "Experiment 4"))+
  scale_fill_manual(values=c(palette[1], palette[2], palette[3])) +
  scale_color_manual(values = c(palette[1], palette[2], palette[3]))

# Summaries
violin_bayes(PSE, HDI_range =  c(0.055, 0.945))[[2]]
# pd
p_direction(PSE.df)
# % in ROPE
rope(PSE.df, ci=1, range=c(-0.1, 0.1))
#---------------------------------------------------------------------------------------------------------------------------
# Contrasts between conditions across experiments
IPEF_IPEG<-PSE$Posterior[PSE$Condition=="IPEF"]-PSE$Posterior[PSE$Condition=="IPEG"]
IPE_IPEG<-PSE$Posterior[PSE$Condition=="IPE"]-PSE$Posterior[PSE$Condition=="IPEG"]
PSE_dif<- cbind.data.frame("IPE-IPEG"=IPE_IPEG,"IPEF-IPEG"=IPEF_IPEG)
PSE_dif.df<-PSE_dif
PSE_dif<- PSE_dif %>% gather("IPE-IPEG","IPEF-IPEG", key= Condition, value= Posterior)
violin_dif<- violin_bayes(PSE_dif, HDI_range = c(0.055, 0.945))[[1]]
violin_dif +
  labs(x="Experment Contrast", y = "Logit")+
  scale_x_discrete(labels=c( "Experiment 2 > Experiment 4", "Experiment 3 > Experiment 4"))+
  scale_fill_manual(values=c(palette[5], palette[6])) +
  scale_color_manual(values = c(palette[5], palette[6]))

# Summaries
violin_bayes(PSE_dif, HDI_range =  c(0.055, 0.945))[[2]]
# pd
p_direction(PSE_dif.df)
# % in ROPE
rope(PSE_dif.df, ci=1, range=c(-0.1, 0.1))

# OR 
posterior_summary(exp(IPE_IPEG), probs=c(0.055, 0.945))
posterior_summary(exp(IPEF_IPEG), probs=c(0.055, 0.945))
```



## Grading effect of prosocial simulation effect 
```{r}
Bayes_gen<- brm(data=IPEG.df, family=cumulative("logit"),
                      bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                              (Match_condition|Story_ID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)) +
                          lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T)


# Diagnostic Checks: pp check and traceplots
pp_check(Bayes_gen);plot(Bayes_gen)
# Rhat and sample sizes
bayes_samples(Bayes_gen)

# Summary
summary(Bayes_gen, prob=1)
# pd
p_direction(Bayes_gen, parameters = "b_Match_condition")
# % in ROPE
rope(Bayes_gen,ci=1, range = c(-0.10, 0.10), parameters ="b_Match_condition")
# Bayes factors for condition contrasts
BF01<- hypothesis(Bayes_gen, hypothesis =c("Match_conditionSMAM - Match_conditionSMAP=0",
                                           "Match_conditionSMAM - Match_conditionSPAM=0",
                                           "Match_conditionSMAM - Match_conditionSPAP=0",
                                           "Match_conditionSMAP - Match_conditionSPAM=0", 
                                           "Match_conditionSMAP - Match_conditionSPAP=0",
                                           "Match_conditionSPAM - Match_conditionSPAP=0" ) , alpha=0.055)
BF01;plot(BF01)

# Extract posterior samples 
set.seed(67);posterior_gen<- posterior_samples(Bayes_gen) 
latent_SD(posterior_gen)
```
### Violn plots
```{r}
gen_effect <- cbind.data.frame("S-A-" = posterior_gen$b_Match_conditionSMAM,
                              "S-A+" = posterior_gen$b_Match_conditionSMAP, 
                              "S+A-" = posterior_gen$b_Match_conditionSPAM, 
                              "S+A+" = posterior_gen$b_Match_conditionSPAP)
gen_effect.df <- gen_effect
gen_effect <- gen_effect %>% gather("S-A-", "S-A+", "S+A-", "S+A+", key = Condition, value = Posterior)
violin_gen <- violin_bayes(gen_effect, HDI_range=c(0.055, 0.945))[[1]]
violin_gen + 
  labs(x = "Condition Contrast", y = "Logit") +
  scale_x_discrete(labels = c("S-A-" = "S-A- > Control", "S-A+" = "S-A+ > Control", "S+A-" = "S+A- > Control", "S+A+" = "S+A+ > Control"))
  
# Summaries
violin_bayes(gen_effect, HDI_range =c(0.055, 0.945))[[2]]
#pd
p_direction (gen_effect.df)
# OR
posterior_summary(exp(gen_effect.df), probs=c(0.055, 0.945))
#-------------------------------------------------------------------------------------------------------------
# Plot the predicted probability of each category on the outcome measure for each condition
Gen_plot<-conditional_effects(Bayes_gen,categorical=T)
plot(Gen_plot)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "S-A-", "S-A+", "S+A-", "S+A+")) +
  theme_classic() +
  xlab("Conditions") +
  ylim (0, 0.45)
#-------------------------------------------------------------------------------------------------------------
# Contrasts between conditions
cond_contrasts <- cbind.data.frame ("S-A-<S-A+" = gen_effect.df$`S-A+` - gen_effect.df$`S-A-`, 
                                    "S-A-<S+A-" = gen_effect.df$`S+A-` - gen_effect.df$`S-A-`,
                                    "S-A-<S+A+" = gen_effect.df$`S+A+` - gen_effect.df$`S-A-`,
                                    "S-A+<S+A-" = gen_effect.df$`S+A-` - gen_effect.df$`S-A+`,
                                    "S-A+<S+A+" = gen_effect.df$`S+A+` - gen_effect.df$`S-A+`,
                                    "S+A-<S+A+" = gen_effect.df$`S+A+` - gen_effect.df$`S+A-`)
colnames(cond_contrasts) <- c("S-A-<S-A+", "S-A-<S+A-","S-A-<S+A+", "S-A+<S+A-", "S-A+<S+A+", "S+A-<S+A+")
cond_contrasts.df<- cond_contrasts
cond_contrasts <- cond_contrasts %>% gather("S-A-<S-A+", "S-A-<S+A-","S-A-<S+A+", "S-A+<S+A-", "S-A+<S+A+", "S+A-<S+A+", key = Condition, value= Posterior)
contrast_plot<- violin_bayes(cond_contrasts, HDI_range=c(0.055, 0.945))[[1]]
contrast_plot + 
  labs(x="Condition Contrast", y = "Logit")
# Summaries
violin_bayes(cond_contrasts, HDI_range=c(0.055, 0.945))[[2]]
# pd and direction
p_direction (cond_contrasts.df)
# % in ROPE
rope(cond_contrasts.df,ci=1, range =c(-0.18, 0.18))
# ORs
posterior_summary(exp(cond_contrasts.df), probs=c(0.055, 0.945))
```



### Order restricted model - with Identify
* Models to be compared
** 1) a null model M0: all conditions (including control) are ~ equal
** 2) Unrestricted model Mu1: Identify != S-A- = S+A- = S-A+ = S+A+
** 3) Unrestricted model Mu2: Identify != S-A- != S+A- != S-A+ != S+A+
** 4) Unrestricted model Mu3: Identify != S-A- = S+A- = S-A+ != S+A+
** 5) ordered model1 M1:  Identify < S-A- = S+A- = S-A+ = S+A+
** 6) ordered model2 (theory driven) M2: Identify < S-A- < S+A- = S-A+ < S+A+
** 7) ordered model3 M3: Identify < S-A- = S+A- = S-A+ < S+A+

```{r}
# Null model 
null<- brm(data= IPEG.df, family=cumulative("logit"), 
                  Help~HT_sex_c+HT_age_c+(1|participant)+
                      (1|Story_ID)+(1|HTFace_ID)+(1|STFace_ID),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T)
# Mu1
Bayes<- brm(data=IPEG.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+HT_sex_c+HT_age_c+(Conditions|participant)+
                      (Conditions|Story_ID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))

# Mu2
Bayes_gen<- brm(data=IPEG.df, family=cumulative("logit"),
                      bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                              (Match_condition|Story_ID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)) +
                          lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T)

IPEG.df<- IPEG.df%>% 
              mutate(ORM_code = ifelse(Match_condition=='Identify', "Identify",
                                  ifelse(Match_condition=='S+A+','S+A+', "Imagine")))
IPEG.df$ORM_code <- as.factor (IPEG.df$ORM_code)
IPEG.df$ORM_code <- relevel(IPEG.df$ORM_code, ref = "Identify")
# Mu3
Bayes_gen2<- brm(data=IPEG.df, family=cumulative("logit"),
                      bf(Help~ORM_code+HT_sex_c+HT_age_c+(ORM_code|participant)+
                              (ORM_code|Story_ID)+(ORM_code|HTFace_ID)+(ORM_code|STFace_ID)) +
                          lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T)
set.seed(67);posterior_mu3<- posterior_samples(Bayes_gen2) 

# Mu1/M0
set.seed(67); BF_Mu1_vs_M0 <- bayes_factor(Bayes, null)
BF_Mu1_vs_M0
# M0/Mu2
set.seed(67);BF_Mu2_vs_M0 <- bayes_factor(Bayes_gen, null)
BF_M0_vs_Mu2<-1/BF_Mu2_vs_M0$bf
# M0/Mu3
set.seed(67);BF_Mu3_vs_M0 <- bayes_factor(Bayes_gen2, null)
BF_M0_vs_Mu3<-1/BF_Mu3_vs_M0$bf

# Ordered Restricted model 1
m1 <- (posterior[, "b_ConditionsImagine"]>0) 
# M1/Mu1
(BF_M1_vs_Mu1 <- restricted_BF(m1, 4e4, 2))

## Ordered Restricted model 2
m2<- (posterior_gen[, "b_Match_conditionSMAM"]>0) &
  (posterior_gen[, "b_Match_conditionSMAP"]-posterior_gen[, "b_Match_conditionSMAM"] > 0) &
  (abs(posterior_gen[, "b_Match_conditionSMAP"]-posterior_gen[, "b_Match_conditionSPAM"]) <= 0.1) |
  (posterior_gen[, "b_Match_conditionSMAP"] > posterior_gen[, "b_Match_conditionSPAM"]) |
  (posterior_gen[, "b_Match_conditionSMAP"] < posterior_gen[, "b_Match_conditionSPAM"]) & 
  (posterior_gen[, "b_Match_conditionSPAP"]-posterior_gen[, "b_Match_conditionSPAM"] > 0)
# M2/Mu2
(BF_M2_vs_Mu2<-restricted_BF(m2, 4e4, 5, 2))

## Order restricted model 3
m3<-(posterior_mu3[, "b_ORM_codeImagine"] > 0) &
    (posterior_mu3[, "b_ORM_codeImagine"] < posterior_mu3[, "b_ORM_codeSPAP"]) &
    (posterior_mu3[, "b_ORM_codeSPAP"] > 0)
(BF_M3_vs_Mu3 <- restricted_BF(m3, 4e4, 3))

# By transitivity
BF_M1_vs_M0<- BF_Mu1_vs_M0$bf * BF_M1_vs_Mu1
BF_M2_vs_M0 <-  BF_M2_vs_Mu2 / BF_M0_vs_Mu2
BF_M3_vs_M0 <- BF_M3_vs_Mu3 * BF_Mu3_vs_M0$bf
BF_M1_vs_M2 <- BF_M1_vs_M0 / BF_M2_vs_M0
BF_M1_vs_M3 <- BF_M1_vs_M0 / BF_M3_vs_M0
BF_M1_vs_Mu2 <- BF_M1_vs_M0 * BF_M0_vs_Mu2
BF_M2_vs_M3 <- BF_M2_vs_M0 / BF_M3_vs_M0
BF_M3_vs_Mu2 <- BF_M3_vs_M0 * BF_M0_vs_Mu2

# BFs
print(paste0("M1/M2: ", BF_M1_vs_M2))
print(paste0("M1/M3: ", BF_M1_vs_M3))
print(paste0("M1/M0: ", BF_M1_vs_M0))
print(paste0("M1/Mu2: ", BF_M1_vs_Mu2))

print(paste0("M2/M3: ", BF_M2_vs_M3))
print(paste0("M2/M0: ", BF_M2_vs_M0))
print(paste0("M2/Mu2: ", BF_M2_vs_Mu2))

print(paste0("M3/M0: ", BF_M3_vs_M0))
print(paste0("M3/Mu2: ", BF_M3_vs_Mu2))

print(paste0("M0/Mu2: ", BF_M0_vs_Mu2))


# I don't think the 1/total permutation prior includes = in the model if it is contrasting to Mu which assumes all condition are dissimilar, so for example permutation of 2 is 2 only A < B and A > B but does not account for A = B
```




### Order restricted model - without Identify
* Models to be compared
** 1) a null model M0: all imagine helping conditions  are ~ equal
** 2) Unrestricted model Mu:  S-A- != S+A- != S-A+ != S+A+
** 3) ordered model2 (theory driven) M1: Identify < S-A- < S+A- = S-A+ < S+A+

```{r}
no_control.df<-IPEG.df[IPEG.df$Match_condition!="Identify",]

# Null model 
null_NC<- brm(data= no_control.df, family=cumulative("logit"), 
                  Help~HT_sex_c+HT_age_c+(1|participant)+
                      (1|Story_ID)+(1|HTFace_ID)+(1|STFace_ID),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T)
# Mu2
Bayes_gen_NC<- brm(data=no_control.df, family=cumulative("logit"),
                      bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                              (Match_condition|Story_ID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)) +
                          lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=67, sample_prior=T,save_all_pars = T)
set.seed(67);posterior_gen_NC<- posterior_samples(Bayes_gen_NC) 

# M0/Mu
set.seed(67);BF_Mu_vs_M0_NC <- bayes_factor(Bayes_gen_NC, null_NC)
(BF_M0_vs_Mu_NC<-1/BF_Mu_vs_M0_NC$bf)


## Ordered Restricted model 1
m1_NC<- (posterior_gen_NC[, "b_Match_conditionSMAP"]>0) &
  (abs(posterior_gen_NC[, "b_Match_conditionSMAP"] - posterior_gen_NC[, "b_Match_conditionSPAM"]) <= 0.1) |
  (posterior_gen[, "b_Match_conditionSMAP"] > posterior_gen[, "b_Match_conditionSPAM"]) |
  (posterior_gen[, "b_Match_conditionSMAP"] < posterior_gen[, "b_Match_conditionSPAM"]) & 
  (posterior_gen_NC[, "b_Match_conditionSPAP"] > posterior_gen_NC[, "b_Match_conditionSPAM"])
# M1/Mu
(BF_M1_vs_Mu_NC<-restricted_BF(m1_NC, 4e4, 4))

# By transitivity 
BF_M1_vs_M0_NC <-BF_M0_vs_Mu_NC / BF_M1_vs_Mu_NC 


# BFs
print(paste0("M0/Mu: ", BF_M0_vs_Mu_NC))
print(paste0("M0/M1: ", BF_M0_vs_M1_NC))
print(paste0("M1/Mu: ", BF_M1_vs_Mu_NC))
```


# order restricted models without random effects
## models
```{r}
# Mu1
Bayes_NR <- brm(data = IPEG.df, family = cumulative("logit"),
                bf(Help ~ Conditions + HT_sex_c + HT_age_c + (1|participant) +
                          (1|Story_ID) + (1|HTFace_ID) + (1|STFace_ID)) +
                lf(disc ~ 0 + Conditions, cmc=F),
                prior = c(prior(normal (0, 1), class = b),
                         prior(normal(0, 1.2), class = Intercept),
                         prior(exponential(1), class = sd)),
                iter = 7000, warmup = 2000, chains = 8, cores = 8, seed = 67, sample_prior = T, 
                save_all_pars = T, control = list(adapt_delta = 0.99))
set.seed(67);posterior_mu1_NR<- posterior_samples(Bayes_NR) 

# Mu2
Bayes_gen_NR<- brm(data = IPEG.df, family = cumulative("logit"),
                   bf(Help ~ Match_condition + HT_sex_c + HT_age_c + (1|participant) +
                             (1|Story_ID) + (1|HTFace_ID) + (1|STFace_ID)) +
                   lf(disc~ 0 + Match_condition, cmc = F),
                   prior= c(prior(normal (0, 1), class = b),
                            prior(normal(0, 1.2), class =Intercept),
                            prior(exponential(1), class = sd)),
                   iter = 7000,warmup = 2000, chains = 8, cores = 8, seed = 67, sample_prior = T, save_all_pars = T)
set.seed(67);posterior_mu2_NR<- posterior_samples(Bayes_gen_NR) 

# Mu3
Bayes_gen2_NR<- brm(data = IPEG.df, family = cumulative("logit"),
                    bf(Help ~ ORM_code + HT_sex_c + HT_age_c + (1|participant) +
                             (1|Story_ID) + (1|HTFace_ID) + (1|STFace_ID)) +
                    lf(disc~  0 + Match_condition, cmc = F),
                    prior= c(prior(normal (0, 1), class = b),
                             prior(normal(0, 1.2), class = Intercept),
                             prior(exponential(1), class = sd)),
                    iter = 7000,warmup = 2000, chains = 8, cores = 8, seed = 67, sample_prior = T,save_all_pars = T)
set.seed(67);posterior_mu3_NR<- posterior_samples(Bayes_gen2_NR) 
```

## models
```{r}
# Mu1/M0
set.seed(67); BF_Mu1_vs_M0_NR <- bayes_factor(Bayes_NR, null)
BF_Mu1_vs_M0_NR
# M0/Mu2
set.seed(67);BF_Mu2_vs_M0_NR <- bayes_factor(Bayes_gen_NR, null)
BF_M0_vs_Mu2_NR<-1/BF_Mu2_vs_M0_NR$bf
# M0/Mu3
set.seed(67);BF_Mu3_vs_M0_NR <- bayes_factor(Bayes_gen2_NR, null)
BF_M0_vs_Mu3_NR<-1/BF_Mu3_vs_M0_NR$bf

# Ordered Restricted model 1
m1_NR <- (posterior_mu1_NR[, "b_ConditionsImagine"] > 0) 
# M1/Mu1
(BF_M1_vs_Mu1_NR <- restricted_BF(m1, 4e4, 2))

## Ordered Restricted model 2
m2_NR <- (posterior_mu2_NR[, "b_Match_conditionSMAM"] > 0) &
         (posterior_mu2_NR[, "b_Match_conditionSMAP"] - posterior_mu2_NR[, "b_Match_conditionSMAM"] > 0) &
         (abs(posterior_mu2_NR[, "b_Match_conditionSMAP"] - posterior_mu2_NR[, "b_Match_conditionSPAM"]) <= 0.1) |
         (posterior_mu2_NR[, "b_Match_conditionSMAP"] > posterior_mu2_NR[, "b_Match_conditionSPAM"]) |
         (posterior_mu2_NR[, "b_Match_conditionSMAP"] < posterior_mu2_NR[, "b_Match_conditionSPAM"]) & 
         (posterior_mu2_NR[, "b_Match_conditionSPAP"] - posterior_mu2_NR[, "b_Match_conditionSPAM"] > 0)
# M2/Mu2
(BF_M2_vs_Mu2_NR <- restricted_BF(m2_NR, 4e4, 5, 2))

## Order restricted model 3
m3_NR<-(posterior_mu3_NR[, "b_ORM_codeImagine"] > 0) &
       (posterior_mu3_NR[, "b_ORM_codeImagine"] < posterior_mu3_NR[, "b_ORM_codeSPAP"]) &
       (posterior_mu3_NR[, "b_ORM_codeSPAP"] > 0)
(BF_M3_vs_Mu3_NR <- restricted_BF(m3_NR, 4e4, 3))

# By transitivity
BF_M1_vs_M0_NR<- BF_Mu1_vs_M0_NR$bf * BF_M1_vs_Mu1_NR
BF_M2_vs_M0_NR <-  BF_M2_vs_Mu2_NR / BF_M0_vs_Mu2_NR
BF_M3_vs_M0_NR <- BF_M3_vs_Mu3_NR * BF_Mu3_vs_M0_NR$bf
BF_M1_vs_M2_NR <- BF_M1_vs_M0_NR / BF_M2_vs_M0_NR
BF_M1_vs_M3_NR <- BF_M1_vs_M0_NR / BF_M3_vs_M0_NR
BF_M1_vs_Mu2_NR <- BF_M1_vs_M0_NR * BF_M0_vs_Mu2_NR
BF_M2_vs_M3_NR <- BF_M2_vs_M0_NR / BF_M3_vs_M0_NR
BF_M3_vs_Mu2_NR <- BF_M3_vs_M0_NR * BF_M0_vs_Mu2_NR

# BFs
print(paste0("M1/M2: ", BF_M1_vs_M2_NR))
print(paste0("M1/M3: ", BF_M1_vs_M3_NR))
print(paste0("M1/Mu2: ", BF_M1_vs_Mu2_NR))
print(paste0("M1/M0: ", BF_M1_vs_M0_NR))

print(paste0("M2/M3: ", BF_M2_vs_M3_NR))
print(paste0("M2/Mu2: ", BF_M2_vs_Mu2_NR))
print(paste0("M2/M0: ", BF_M2_vs_M0_NR))

print(paste0("M3/Mu2: ", BF_M3_vs_Mu2_NR))
print(paste0("M3/M0: ", BF_M3_vs_M0_NR))

print(paste0("Mu2/M0: ", 1/BF_M0_vs_Mu2_NR))
```





## Vividness
```{r}
# Detail
IPEG_det_IH <- brm(data = vivid.df, family = cumulative("logit"),
                      formula = bf(Help ~ Detail_C + HT_sex_c + HT_age_c + (Detail_C|participant) +
                      (Detail_C|Story_ID) + (Detail_C|HTFace_ID) + (Detail_C|STFace_ID)),
                  prior = c(prior(normal(0,1), class = b),
                            prior(normal(0,1.2), class = Intercept),
                            prior(exponential(1), class = sd),
                            prior(lkj(1), class = cor)),
                  iter = 7000 ,warmup = 2000, chains = 8, cores = 8, seed = 67, sample_prior = T,save_all_pars = T)

pp_check(IPEG_det_IH)
bayes_samples(IPEG_det_IH)
# Summary
summary(IPEG_det_IH, prob = 0.89)
# pd
p_direction(IPEG_det_IH, parameters = c("b_Detail_C"))
# Extract posterior samples 
set.seed(67);posterior_det_IPEG <- posterior_samples(IPEG_det_IH)
# OR
posterior_summary(exp(posterior_det_IPEG$`b_Detail_C`), probs=c(0.055, 0.945))
#------------------------------------------------------------------------------------------------------------------------
# Coherence
IPEG_coh_IH <- brm(data = vivid.df, family = cumulative("logit"),
                      formula = bf(Help ~ Coherence_C + HT_sex_c + HT_age_c + (Coherence_C|participant) +
                      (Coherence_C|Story_ID) + (Coherence_C|HTFace_ID) + (Coherence_C|STFace_ID)),
                  prior = c(prior(normal(0, 1), class = b),
                            prior(normal(0, 1.2), class = Intercept),
                            prior(exponential(1), class = sd),
                            prior(lkj(1), class = cor)),
                  iter = 7000 ,warmup = 2000, chains = 8, cores = 8, seed = 67, sample_prior = T,save_all_pars = T)

pp_check(IPEG_coh_IH)
bayes_samples(IPEG_coh_IH)
# Summary
summary(IPEG_coh_IH, prob = 0.89)
# pd
p_direction(IPEG_coh_IH, parameters = c("b_Coherence_C"))
# Extract posterior samples 
set.seed(67);posterior_coh_IPEG <- posterior_samples(IPEG_coh_IH)
# OR
posterior_summary(exp(posterior_coh_IPEG$`b_Coherence_C`), probs=c(0.055, 0.945))
```

#### Plots
```{r}
# Violin plots -- Detail and Coherence
IPEG_vivid <- cbind.data.frame('Detail' = posterior_det_IPEG$b_Detail_C, "Coherence" = posterior_coh_IPEG$b_Coherence_C)
plot_vivid_IPEG <- IPEG_vivid %>% gather("Detail", "Coherence",  key = Condition, value = Posterior)
violin_vivid_IPEG <- violin_bayes(plot_vivid_IPEG, HDI_range = c(0.055, 0.945))[[1]]
violin_vivid_IPEG +
  labs(x = "Vividness measures", y = "Logit") +
  theme(legend.position='none') +
  ylim(-0.5, 1) +
  scale_fill_manual(values = c(palette[2], palette[3])) +
  scale_color_manual(values = c(palette[2], palette[3]))

# Summary
violin_bayes(plot_vivid_IPEG, HDI_range = c(0.055, 0.945))[[2]]
# pd 
p_direction(IPEG_vivid)
# OR
posterior_summary(exp(IPEG_vivid), probs = c(0.055, 0.945))
```





















